---
title: "Data 607 Tidyverse Extend Assignment"
author: "Sung Lee"
date: "4/20/2020"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
theme: lumen
number_sections: yes
---

[Assignment on RPubs](https://rpubs.com/logicalschema/data607_extend "Sung's Rpub Extend Assignment")
<br>
[Create Rmd on Github](https://github.com/acatlin/SPRING2020TIDYVERSE/blob/master/munguia_stringr.Rmd "Michael Munguia's Create Assignment Github")  
[Extend Rmd on Github](https://github.com/acatlin/SPRING2020TIDYVERSE/blob/master/Sung_Lee_extend_munguia_stringr.Rmd "Sung Lee's Extend Assignment Github")  


# Purpose  

This project is to extend Michael Munguia's `stringr` CREATE project. It will provide additional demonstration functions for the `stringr` package.


# Data  

This Rmd will employ Michael's csv data that is already a part of this repository. The csv file is `endorsements-2020.csv` and resides at this link: https://raw.githubusercontent.com/acatlin/SPRING2020TIDYVERSE/master/endorsements-2020.csv.  

Let's setup the initial libraries.

```{r}

# Setup of the initial libraries for this demo
library(dplyr)
library(stringr)

# The repo variable is the SPRING2020TIDYVERSE repository
repo <- "https://raw.githubusercontent.com/acatlin/SPRING2020TIDYVERSE/master/"

```  

<br>
We will read in the csv that resides in the repository.


```{r, message=FALSE}

# Imports the csv as a dataframe
(df <- readr::read_csv(paste0(repo, "endorsements-2020.csv")))
```


# Helpful Functions {.tabset}

Michael's project demonstrated the use of `str_detect`, `mutate_at`, `str_replace`, `str_split`, `select`, and `filter`. I will look at two functions.

<br>

## str_replace_na 

Let's look at the function `str_replace_na`. This function is able to replace `NA` values with a suitable replacement string. Let's create a new dataframe where `NA` values in the city column are replaced with the string "Not Available".

```{r}

# Creates a new dataframe where NA is replaced with "Not Available"
(city_df <- df %>% mutate_at("city", str_replace_na, "Not Available"))

```

<br>


## str_to_upper  

The function `str_to_upper` converts a string to upper case letters. This function may be handy for future text wrangling.

Let's capitalize the data in the `position` column using this function.  


```{r}

# Creates a new dataframe where position is capitalized
(capitalize_position_df <- df %>% mutate_at("position", str_to_upper, "en"))

```  

<br>

# Conclusion  

`stringr` provides handy functions to wrangle data. More information about `stringr` can be found here: https://cran.r-project.org/web/packages/stringr/stringr.pdf  

